Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-27 EconGrowth.Rnw
Now creating much better graph for the factors of production. Colors are all black, lines are the way I want them. Beginning work on developing a GDP comparison graph.

<<creategraph>>=

createCountryInputGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graph <- xyplot(iGDP+iQ+iX+iU ~ iYear, data=dataTable,
                  type="l",
                  scales=list(cex=1.5, tck=-1),
                  ylab="Indexed (1980=1)",
                  auto.key=list(columns=1))
  return(graph)
}

createCountryInputGraph("US")

>>>>

<<graphs>>=

createCountryFactorsGraph <- function(countryName){
  dataTable <- loadData(countryName)
  lineSpec <- list(lty=c(1, 5, 2, 4), #line type
                   col=c("black", "black", "black", "black"), #line colors
                   lwd=c(1, 1, 1, 1)) #line widths
  graph <- xyplot(iCapStk+iLabor+iQ+iX ~ iYear, data=dataTable,
                  key=list(text=list(c("k", "l", "q", "x")),
                           type="l",
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  type="l",
                  par.settings = list(superpose.line = lineSpec),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}

createGDPComparisonGraph <- function(countryName){
  dataTable <- loadData(countryName)
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=c(1, 1, 5, 2, 4), #line type
                   col=colors,
                   lwd=c(0, 1, 1, 1, 1)) #line widths. 0 suppresses the line for historical GDP.
  pointSpec <- list(col=colors)
  graph <- xyplot(iGDP ~ iYear, data=dataTable,
                  key=list(text=list(c("GDP")),
                           type="b",
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  type="b",
                  par.settings = list(superpose.line = lineSpec),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)

}

createGDPComparisonGraph("US")

#createCountryFactorsGraph("US")
#lapply(countries, createCountryFactorsGraph)
